Portfolio conservation of metapopulations under\\climate change

### 2014-08-04 inst/ms/appendices/Appendix-A.tex
Add back 2 appendices

\documentclass[12pt]{article}

@@

\textsc{Appendix A.} The \texttt{metafolio} \textsf{R} package.

@@

The \texttt{metafolio} \textsf{R} package contains the functions and code to carry out the analyses in our paper. \texttt{metafolio}. The package can be installed from CRAN with:

\begin{verbatim}
install.packages("metafolio")
\end{verbatim}

%Alternatively, you can view the code and install the package from\\ \texttt{http://github.com/seananderson/metafolio}
%\bigskip

The included vignette describes the package and illustrates some example simulations. You can view the vignette with:

\begin{verbatim}
vignette("metafolio")
\end{verbatim}

You can view the help for the package with:

\begin{verbatim}
?metafolio
help(package = "metafolio")
\end{verbatim}

The figures from this paper can be re-created by downloading the code from GitHub and sourcing the file \texttt{README.R} in the \texttt{inst/examples} folder:

\begin{verbatim}
setwd("metafolio/inst/examples")
source("README.R")
\end{verbatim}

>>>>

\documentclass[12pt]{article}
\usepackage{graphicx}

@@

\textsc{Appendix A.} An example straying matrix.

@@

\includegraphics[width=3.5in]{Fig-A1}\\
\textsc{Fig.~A1.} An example straying matrix. The rows and columns represent different populations (indicated by population number). Dark blue indicates a high rate of straying and light blue indicates a low rate of straying.

### 2014-08-04 inst/ms/appendices/Appendix-D.tex
Reduce fig size
Add back 2 appendices

\textsc{Appendix C.} An example straying matrix.

@@

\includegraphics[width=3.5in]{Fig-C1}\\
\textsc{Fig.~C1.} An example straying matrix. The rows and columns represent different populations (indicated by population number). Dark blue indicates a high rate of straying and light blue indicates a low rate of straying.

>>>>

\textsc{Appendix D.} Example simulated time series from alternative conservation scenarios.

@@

\clearpage

\includegraphics[width=4.3in]{Fig-D1}\\
\textsc{Fig.~D1.} Conserving a \textbf{full range} of response diversity (spatial conservation strategy) with \textbf{short-term} environmental fluctuations. This is the same as Fig.~3 but in colour.
\clearpage

\includegraphics[width=4.3in]{Fig-D2}\\
\textsc{Fig.~D2.} Conserving \textbf{one half} of response diversity (spatial conservation strategy) with \textbf{short-term} environmental fluctuations.
\clearpage

\includegraphics[width=4.3in]{Fig-D3}\\
\textsc{Fig.~D3.} Conserving a \textbf{full range} of response diversity (spatial conservation strategy) with \textbf{long-term} environmental change.
\clearpage

\includegraphics[width=4.3in]{Fig-D4}\\
\textsc{Fig.~D4.} Conserving \textbf{one half} of response diversity (spatial conservation strategy) with \textbf{long-term} environmental change.
\clearpage

\includegraphics[width=4.3in]{Fig-D5}\\
\textsc{Fig.~D5.} \textbf{Two populations} conserved with random response diversity and \textbf{short-term} environmental fluctuations.
\clearpage

\includegraphics[width=4.3in]{Fig-D6}\\
\textsc{Fig.~D6.} \textbf{Sixteen populations} conserved with random response diversity and \textbf{short-term} environmental fluctuations.
\clearpage

\includegraphics[width=4.3in]{Fig-D7}\\
\textsc{Fig.~D7.} \textbf{Two populations} conserved with random response diversity and \textbf{long-term} environmental change.
\clearpage

\includegraphics[width=4.3in]{Fig-D8}\\
\textsc{Fig.~D8.} \textbf{Sixteen populations} conserved with random response diversity and \textbf{long-term} environmental change.
\clearpage

\includegraphics[width=4.3in]{Fig-D9}\\
\textsc{Fig.~D9.} \textbf{Two populations} conserved with random response diversity and \textbf{long-term declining stream flow}.
\clearpage

\includegraphics[width=4.3in]{Fig-D10}\\
\textsc{Fig.~D10.} \textbf{Sixteen populations} conserved with random response diversity and \textbf{long-term declining stream flow}.
